How to Avoid OOTA Without Really Trying

### 2024-09-13 paper/ootavacuous.tex
ootavacuous: Fix Listing 3 discussion
Suggested-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

On the other hand, OOTA cycles need not involve nonsensical or
unmotivated values, as shown in
Listing~\ref{lst:OOTA Cycle}.
Line~3 of both processes stores the value 42 only when line~2 determines
that the value loaded was 42.
This, combined with the default-zero initialization, explains why this
OOTA result has not been observed on real implementations.

>>>>

On the other hand, OOTA cycles need not involve nonsensical or
unmotivated values, as shown in
Listing~\ref{lst:OOTA Cycle}.
Line~3 of both processes stores the value 42 only when line~2 determines
that the value loaded was 42.
As with Listing~\ref{lst:Simple OOTA}, hardware ordering prevents the
OOTA result, as discussed further in
Section~\ref{sec:Hardware Dependencies, Instruction Ordering, and the Fundamental Property}.
